Check Coverage

### 2019-08-08 analysis/merge_data.Rmd
debug fd calculation with joggle

  trait_mat <- data %>%
    select(-c(id, taxa, record_id, day, month, year, sample_desc, id_species, 
              latitude, longitude, sum_abundance, sum_biomass, sourceName, scientificName)
    ) %>%
    distinct() %>%
    select_if(~ length(unique(.)) > 1) %>% #remove columns that have the same value for all columns
    mutate_at(vars(-id), list(~scales::rescale(.,to=c(0, 1)))) %>% #rescale variables
    arrange(id) %>%
    column_to_rownames("id")

@@

get_fd_safe <- possibly(get_fd, NA)

test_data <- biotime_traits %>% 
  group_by(study_id, plot) %>%
  nest() %>%
  mutate(metrics = map(data, ~get_fd_safe(.x))) %>%
  filter(!is.na(metrics)) %>%
  select(-data) %>%
  unnest()
```

>>>>

  trait_mat <- data %>%
    select(-c(taxa, record_id, day, month, year, sample_desc, id_species, 
              latitude, longitude, sum_abundance, sum_biomass, sourceName, scientificName)
    ) %>%
    distinct() %>%
    select_if(~ length(unique(.)) > 1) %>% #remove columns that have the same value for all columns
    mutate_at(vars(-id, -diet_5cat), list(~scales::rescale(.,to=c(0, 1)))) %>% #rescale variables
    arrange(id) %>%
    column_to_rownames("id")

@@

#get_fd_safe <- possibly(get_fd, NA)

test_data <- biotime_traits %>% 
  group_by(study_id, plot) %>%
  nest() %>%
  mutate(metrics = map(data, ~get_fd(.x))) %>%
  select(-data) %>%
  unnest()
```
